% ---------- Contact ----------
\newcommand{\Phone}{+36 30 555 8877}
\newcommand{\Location}{Ebes, Hungary}

% ---------- UI text ----------
\newcommand{\TxtExperience}{Experience}
\newcommand{\TxtProjects}{Projects}
\newcommand{\TxtSummary}{who am I?}
\newcommand{\TxtSkills}{Skills}
\newcommand{\TxtLanguages}{Languages}
\newcommand{\TxtEducation}{Education}
\newcommand{\TxtInterests}{Interests}

% ---------- Sections ----------
% Experience section
% Experience 1
\newcommand{\ExpATitle}{Full Stack Developer}
\newcommand{\ExpAEmployer}{Monky Shine}
\newcommand{\ExpADate}{April 2023 -- Ongoing}
\newcommand{\ExpAType}{Part Time}
\newcommand{\ExpALocation}{Aalborg}
\newcommand{\ExpAContent}{
    \begin{itemize}
        \item[] \justifying Develop and maintain the company's booking application using Angular and .NET Core. I have implemented new features, improved existing functionality and contributed to the integration of Nets payment to streamline transactions and enhance user experience.
        \item[] \color{black}\texttt{C\# | .NET Core | Angular | TypeScript | MSSQL | SCSS}
    \end{itemize}
}

% Experience 2
\newcommand{\ExpBTitle}{Game Developer}
\newcommand{\ExpBEmployer}{EmptyBox}
\newcommand{\ExpBDate}{January 2023 -- April 2023}
\newcommand{\ExpBType}{Internship}
\newcommand{\ExpBLocation}{Aalborg}
\newcommand{\ExpBContent}{
    \begin{itemize}
        \item[] \justifying Worked on migrating an unreleased project to Unity DOTS, improving performance and scalability. Developed core systems for the project, including a 2D animation system for Unity DOTS, and a fast-travel system.
        \item[] \color{black}\texttt{Unity | C\# | Unity DOTS}
    \end{itemize}
}

% Experience 3
\newcommand{\ExpCTitle}{Software Developer}
\newcommand{\ExpCEmployer}{OleSoft}
\newcommand{\ExpCDate}{August 2020 -- October 2020}
\newcommand{\ExpCType}{Internship}
\newcommand{\ExpCLocation}{Debrecen}
\newcommand{\ExpCContent}{
    \begin{itemize}
        \item[] \justifying Contributed to a web application that digitized the process of trash container rentals, significantly reducing manual paperwork and improving efficiency.
        \item[] \color{black}\texttt{React | TypeScript | Node.js}
    \end{itemize}
}

% Projects section
% Project 1
\newcommand{\ProjAName}{StarCraft II Intelligent Agent}
\newcommand{\ProjAContext}{Master's Project}
\newcommand{\ProjAContent}{
    \begin{itemize}
        \item[] \justifying Developed an intelligent agent capable of playing StarCraft II. The agent utilized Monte-Carlo Tree Search for Action selection and Neural Networks to analyze the state of the game.
        \item[] \color{black}\texttt{Python | C++}
    \end{itemize}
}

% Project 2
\newcommand{\ProjBName}{Graphite - A Custom Language for Graph Manipulation}
\newcommand{\ProjBContext}{University Project}
\newcommand{\ProjBContent}{
    \begin{itemize}
    \sloppy
        \item[] \justifying Designed and implemented Graphite, a custom object-oriented programming language focused on simplifying graph manipulation with specialized operations and enabling graph visualization through DOT integration.
        \item[] \color{black}\texttt{C\# | DOT | Graphviz}
    \end{itemize}
}

% Project 3
\newcommand{\ProjCName}{Player Programmable Behaviours}
\newcommand{\ProjCContext}{Bachelor's Project}
\newcommand{\ProjCContent}{
    \begin{itemize}
        \item[] \justifying Developed a system which allows developers to expose the code of objects, allowing players to interactively modify in-game behaviour through a custom C-like scripting language.
        \item[] \color{black}\texttt{C\# | Unity}
    \end{itemize}
}

% Summary section
\newcommand{\SummaryContent}{
    \begin{justify}
    \sloppy
    Newly graduated software developer looking for new challenges and opportunities to learn and grow professionally. I enjoy learning new technologies by solving problems and working on projects, be it personal or professional. Outside of work, I use my skills to develop games and build tools for my hobbies.
    \end{justify}
}

% Skills section
\newcommand{\SkillProgramming}{Programming}
\newcommand{\SkillAdvanced}{Advanced}
\newcommand{\SkillIntermediate}{Intermediate}
\newcommand{\SkillBeginner}{Beginner}
\newcommand{\SkillFrameworksTools}{Frameworks \& Tools}

% Languages section
\newcommand{\LangHungarian}{Hungarian}
\newcommand{\LangEnglish}{English}

% Education section
% Education 1
\newcommand{\EduAName}{M.Sc.\ in Computer Science}
\newcommand{\EduAInstitution}{Aalborg University}
\newcommand{\EduADate}{September 2023 -- June 2025}

% Education 2
\newcommand{\EduBName}{B.Sc.\ in Software Development}
\newcommand{\EduBInstitution}{University College of Northern Denmark}
\newcommand{\EduBDate}{January 2022 -- June 2023}

% Education 3
\newcommand{\EduCName}{AP\ in Computer Science}
\newcommand{\EduCInstitution}{University College of Northern Denmark}
\newcommand{\EduCDate}{September 2018 -- December 2020}

% Education 4
\newcommand{\EduDName}{High School Diploma}
\newcommand{\EduDInstitution}{Mechwart András Secondary Technical School of Engineering and Information Technology}
\newcommand{\EduDDate}{September 2014 -- June 2018} 

% Interests section
\newcommand{\InterestsContent}{
    \begin{itemize}
    \item Playing and developing games
    \item Running and Cycling
    \item Reading
    \end{itemize}
}